---
title: "My GGPlot Experiments
output: github_document
---

## Giving This a Shot

I'll put my notes here, followed by code:

So I can do a scatterplot by more or less using the following code ...

```{scatterplot}
p <- ggplot(data= ... , mapping=aes(x= ... , y= ... ))
p+geom_point()
```

... but replacing ellipses with the data source and the specific X and Y axes for my plot.

To get a smoother line in addition to the plot, I simply use:

```{smoothed scatterplot}
p+geom_point()+geom_smooth()
```
And to make it a logorithmic axis (if I'm feeling really nerdy):

```{logarithmic scatterplot}
p+geom_point()+geom_smooth(method="gam")+scale_x_log10()
```

This is a plot with a logarithmic scale, converted to currency, colored purple:

```{log color scale example}

p+geom_point(color="purple")+geom_smooth(method="loess")+scale_x_log10(labels=scales::dollar)
```

An example of semitransparent dots and a different-colored, thicker line:

```{more variables example}
p + geom_point(alpha=0.3)+geom_smooth(color="orange", se=FALSE, size=3, method="lm")+scale_x_log10()
```

A full chart, with title, subtitle, source, correct scale labels:

```{r full chart part 1}
p <- ggplot(data=gapminder, mapping=aes(x=gdpPercap, y=lifeExp))
```

```{r full chart part 2}
p+geom_point(alpha=0.3)+geom_smooth(method="gam")+scale_x_log10(labels=scales::dollar)+labs(x="GDP per Capita", y="Life Expectancy in Years", title="Economic Growth and Life Expectancy", subtitle="Data points are country-years", caption="Source: Gapminder")
```
... And this is what turns up, right here, when I run it through RMD instead of the console!

## Plotting ... A MURDER

I'll put my devious plots here.

Here is the basic CoC v. Dem scatterplot:

```{r my plot}
read_csv("CongsxDems.csv")

ptib <- as_tibble(p)

p <- ggplot(data=ptib, mapping=aes(x=Percentage, y=Dems))

p+geom_point()
```

And here is the fancier version with a smoothed line, title and labels:

```{r my fancy plot}
read_csv("CongsxDems.csv")

ptib <- as_tibble(p)

p <- ggplot(data=ptib, mapping=aes(x=Percentage, y=Dems))

p+geom_point()+geom_smooth(method="gam")+labs(x="Cities with Churches of Christ, 1976", y="Vote for Joe Biden, 2020", title="Churches of Christ in 1976 vs. Democratic Support in 2020", subtitle="States with a higher share of cities containing at least one Church of Christ in 1976 tended to be less supportive of Democrats in 2020.", caption="Sources: Firm Foundation, Politico")

```
Using tribbles seems to cause problems for R Markdown, however.

count <- p %>% 
  group_by(Year) %>%
  count(Year, Type, State) %>%
  filter (n > 10) %>%
  filter (!State == "*France")